Who introduced the bug? The importance of the previous commit

### 2016-01-25 paperMSR.tex

\maketitle
\begin{abstract}
\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit. However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects which present this characteristic.}

\textbf{In this paper, in order to ascertain the validity of such a claim, we have conducted an observational study that involved bug notifications from a very active project such as OpenStack, in which their source code is continuously evolving. Our results are promising in indicating that exists bug fixed which were not introduced in the previous commit.}
\end{abstract}

@@

\subsection{Fist Stage}
\label{sec:resultsFS}
We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers, 
\begin{table*}
\centering
%\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table*}

@@

\section{Discussion}
\label{sec:discussion}
This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.

>>>>

\maketitle
\begin{abstract}
To fix a bug in a certain software product, some parts of its source code are modified. At first glance, it could seem reasonable that the fixed bug was introduced by the previous modification of those same parts of the source code (the previous commit). In fact, many studies on bug seeding start with this assumption. However, there is little empirical evidence supporting this assumption, and there are reasons to suppose that in some cases the bug was introduced by other actions, such as an older modification, or a change in called APIs.

This paper tries to shed some light on this area, by analyzing the relationship of bug fixes with their previous commits. To this end, we conducted an observational study on bug reports, their fixes, and their correspoonding previous commits for OpenStack. Our results show that the mentioned asumption does not hold for a large fraction of the analyzed bugs, which were not introduced by their previous commit.
\end{abstract}

@@

\subsection{Fist Stage}
\label{sec:resultsFS}

We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron. The table \ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,

\begin{table*}
\centering
%\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{lllll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table*}

@@

\section{Discussion}
\label{sec:discussion}

This section presents first the threats to the validity of our study. Then, it discusses the possible applications and introduces the work that still has to be done.
